---
output: 
  github_document:
bibliography: inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vICC: Varying Intraclass Correlation Coefficients

[![Build Status](https://travis-ci.org/donaldRwilliams/BGGM.svg?branch=master)](https://travis-ci.org/donaldRwilliams/BGGM)

The goal of vICC is to compute varying intraclass correlation coefficients (ICC) in a one-way random
effects model (i.e., a random intercepts only model). Often computing the ICC is the first step
when fitting a mixed-effects (a.k.a., hierarchical, multilevel, etc.) model that results in *merely* 
one value that is assumed to apply to each group (e.g., person, school). The underlying assumption
is a common within-group variance, whereas in **vICC** a random-effects model is fitted to 
the residual variance, thereby permitting group-level ICCs. When subjects are the grouping variable, this 
is akin to investigating individual differences in the ICC.


## Measurement Reliability
The methodology in **vICC** was introduced in @williams2019putting. The context was 
measurement reliability in a cognitive inhibition task. To this end, **vICC** provides 
ICC(1), that is correlation for any two observations from the same group, and ICC(2), 
this is average score reliability. Both ICC(1) and ICC(2) are reliability indices. 


## Installation

You can install the released version of vICC from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("vICC")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("donaldRwilliams/vICC")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(vICC)
## basic example code
```


